Stack Safety as a Security Property

### 2020-07-08 main.tex
More compact/formal phrasing of Definition 6.5

\definition{Eager testing property}
  Let $\callmap$ a call map and $\codemap$ a function map. Given a state
  $(\mach, \pol) \in \MPS$ that is well-formed w.r.t. a variant stack $\vs$, we
  say that an MP-trace induced from $(\mach, \pol)$ satisfies the \emph{eager
  testing property} at a given call depth if:

@@

  \item If
    %
    (1) the machine takes a \emph{non-call, non-return step} $(\mach,
    \pol) \hookrightarrow_P (\mach', \pol', \obs)$ and the variant stack steps
    to $\vs \hookrightarrow \vs'$,
    %
    (2) the variant stack test $\mathit{\vs}_T ~
    (\mach, \pol) ~ \vs$ is satisfied, and
    %
    (3) the stack safety test
    $\mathit{stack}_T ~ d ~ \MPT ~ \vs'$ is coinductively satisfied at depth $d$
    and for a trace starting continuing after the step, $\head(\MPT) = (\mach',
    \pol')$,
    %
    {\em then} we conclude $\mathit{stack}_T d ~ ((\mach, \pol) : \MPT) ~ vs$.
    \rb{omitting stack size condition}

  \item
%
    If (1) the machine takes a \emph{call step} $(\mach, \pol) \hookrightarrow_P
    (\mach', \pol', \obs)$ and the variant stack steps to $\vs \hookrightarrow
    \vs'$,
%
    (2) $\mathit{\vs}_T ~ (\mach, \pol) ~ \vs$,
%
    (3) for the new contour at the call, $\contour$, \rb{definition?} the
    machine satisfies the stack integrity test $\mathit{int}_T ~ \contour ~
    \mach ~ \mach'$ and the stack confidentiality test with regard to any
    variant $\mathit{variant} ~ C ~ \mach ~ \mach_{\mathit{var}}$,
    $\mathit{conf}_T ~ \mach ~ \mach_{\mathit{var}}$ \rb{definition?},
%
    and (4) the stack safety test is coinductively satisfied at depth $d$ for a
    continuing trace $\MPT$ where $\head(\MPT) = (\mach', \pol')$ after an
    arbitrary variant machine derived from $\contour$ has been added to the top
    of the stack, $\mathit{stack}_T ~ d ~ \MPT ~ (\vse : \vs')$, \rb{define
      $\vse$}
%
    {\em then} we conclude $\mathit{stack}_T ~ d ~ ((\mach, \pol) : \MPT) ~ vs$.

@@

  \item If the machine takes a \emph{return step} at the top of the variant stack
    $(\mach, \pol) \hookrightarrow_P (\mach', \pol', \obs)$,
    the property holds for a trace $(\mach, \pol) \cdot \MPT$ at depth $d$
    if (in addition to the general step conditions)
    the property recurses at depth $d$ with trace $\MPT$
    after removing the returning top variant from the stack.

  \item If the machine takes \emph{simultaneous return-call step}, that is, the
    instruction to which execution returns immediately after completing a call
    is itself a call instruction, the last two cases are combined.

>>>>

\definition{Eager testing property}
  Let $\callmap$ a call map and $\codemap$ a function map. Given a state
  $(\mach, \pol) \in \MPS$ that is well-formed w.r.t. a variant stack $\vs$, we
  say that an MP-trace induced from $(\mach, \pol)$ satisfies the \emph{eager
  testing property} at a given call depth as follows.
% Refactor repetitive notation before case split
  In all cases that assume a machine step, $(\mach, \pol) \hookrightarrow_P
  (\mach', \pol', \obs)$, assume also (unless the step is a return) that the
  variant stack can step, $\vs \hookrightarrow \vs'$, i.e., all its variant
  machines can step.

@@

  \item If
%
    (1) the machine takes a \emph{non-call, non-return step},
%
    (2) the variant stack test $\mathit{\vs}_T ~ (\mach, \pol) ~ \vs$ is
    satisfied, and
%
    (3) the stack safety test $\mathit{stack}_T ~ d ~ ((\mach', \pol') : \MPT) ~
    \vs'$ is coinductively satisfied % at depth $d$
    %% and for a trace starting continuing after the step, $\head(\MPT) = (\mach',
    %% \pol')$,
%
    {\em then} we conclude $\mathit{stack}_T ~ d ~ ((\mach, \pol) : (\mach',
    \pol') : \MPT) ~ vs$.
    %% \rb{omitting stack size condition}

  \item
%
    If (1) the machine takes a \emph{call step} and $\contour$ is the contour at
    the call,
%
    (2) the variant stack test $\mathit{\vs}_T ~ (\mach, \pol) ~ \vs$ is
    satisfied,
%
    (3) the stack integrity test $\mathit{int}_T ~ \contour ~ \mach ~ \mach'$ is
    satisfied and the stack confidentiality test $\mathit{conf}_T ~ \mach ~
    \vm{\contour}$ is satisfied with regard to an arbitrary $\contour$-variant
    of $\mach$,
%
    and (4) the stack safety test $\mathit{stack}_T ~ d ~ ((\mach', \pol') :
    \MPT) ~ (\vm{\contour} : \vs')$ is coinductively satisfied, for an arbitrary
    $\contour$-variant of the machine,
%
    {\em then} we conclude $\mathit{stack}_T ~ d ~ ((\mach, \pol) : (\mach',
    \pol') : \MPT) ~ vs$.

@@

  \item
%
    If (1) the machine takes a \emph{return step} at the top of the variant
    stack (and only the top variant),
%
    (2) the variant stack test $\mathit{\vs}_T ~ (\mach, \pol) ~ \vs$ is
    satisfied,
%
    (3) the stack safety test $\mathit{stack}_T ~ d ~ ((\mach', \pol') : \MPT) ~
    \mathit{tail}(\vs)$ is coinductively satisfied
%
    {\em then} we conclude $\mathit{stack}_T ~ d ~ ((\mach, \pol) : (\mach',
    \pol') : \MPT) ~ vs$.

  \item If the machine takes \emph{simultaneous return-call step}, that is, the
    instruction to which execution returns immediately after completing a call
    is itself a call instruction, the \emph{call step} and \emph{return step}
    cases are combined.
